---
title: "Criterios de exclusión estáticos"
output: 
  html_document:
    code_folding: show
    highlight: espresso
    css: style.css
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes  
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3     
editor_options: 
  chunk_output_type: inline
---


```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                       dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center", 
                      fig.width = 12,
                      fig.height = 12)
```

```{r librerias, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
source_rmd("0_b_funciones.rmd")
}

```

# Análisis de supervivencia

***

```{r}
# cargar lista----------------------------------------------------------------
lista_vm2_fih1 <- readRDS(file.path("Resultados", "lista_vm2_fih1.RDS")) %>% 
  keep(~is.tbl(.))

lista_vm3_fih1 <- readRDS(file.path("Resultados", "lista_vm3_fih1.RDS")) %>% 
  keep(~is.tbl(.))

```

```{r}
# función que realiza el análisis de supervivencia-----------------------------
f_analisis <- function(lista) {
  # pasar de lista a un tibble (name indica el número de tiempo_0)
  base_analisis <- enframe(lista) %>%
    rename(target_trial_number = name) %>% 
    unnest(value)

  print("tabla contingencia exposiciones/casos:")    
  print(base_analisis %>% 
    janitor::tabyl(exposicion, caso) %>%
    janitor::adorn_totals(where = c("row", "col")) %>% 
    janitor::adorn_title())

  base_analisis <- base_analisis %>% mutate(survtime = date_end - date_start)
  base_analisis %>% count(survtime, exposicion)
    
  fit <- survfit(Surv(survtime, caso) ~ exposicion, data = base_analisis) # , subset=survtime>7


print(ggsurvplot(fit, data = base_analisis, xlab = "days of follow-up",
           ylab = "Survival probability",
           main = "Product-Limit Survival Estimates", ylim = c(0.985, 1), 
           risk.table = TRUE, conf.int = TRUE))

## hay que resolver mejor esto de hacer el cox sobre un intervalo.. (a partir del dia 7).. aqui solo indico que se le agrege 7 dias al start (pero no he excludio los casos que aparecen en esos primeros 7 dias!!)
### cox
  cpp = coxph(formula = Surv(survtime, caso) ~ exposicion, 
            data = base_analisis, subset = survtime > 7)
  print("# Estimated effectiveness in Spain from day 7 to 34 after a booster was: 
        51·3% (95% CI 50·2–52·4)")
  print(paste0("# Estimated effectiveness in Navarra was :",
                round((1 - exp(coef(cpp))) * 100, 1), "% (", 
                round((1 - exp(confint((cpp)))[2]) * 100, 1), "-",
                round((1 - exp(confint((cpp)))[1]) * 100, 1), ")"))
}

```


```{r}
# ejecutamos el análisis-------------------------------------------------------
f_analisis(lista = prueba_matching_purrr_2)

```

Este resultado índica que la vacuna es muy efectiva contra las hospitalizaciones.

```{r}
f_analisis(lista = lista_vm3_fih1)

```


```{r}
# comprobaciones outcomes
pobana_2 %>% count(is.na(fih1))
pobana_2 %>% ggplot(aes(x = fih1)) +
  geom_histogram()
pobana_2 %>% count(is.na(fcv1))

```

# Programar la replicación completa del articulo

***

## Table 1: Baseline characteristics of the matched study population

grupos de edad, genero, Number of previous SARS-CoV-2 tests, Primary vaccine schedule, Booster dose, Time since completion of primary vaccine schedule [80-150, 151-180, >180]

## Table 2: Estimated effectiveness of an mRNA COVID-19 vaccine booster in individuals* who had completed primary vaccination schedule against COVID-19

Analyses based on 2 083 857 matched pairs who remained under follow-up by day 7 after the booster dose. Overall, Age group (years): [40–59, 60–79, ≥80], Sex, Type of previous vaccination, Time since vaccination completed, Type of booster [mRNA-1273,BNT162b2]
 # Booster group [Events| Risk per 10 000 individuals] No booster group [Events| Risk per 10 000 individuals]  1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

## Table 3: Sensitivity analyses of vaccine effectiveness 7–34 days after an mRNA COVID-19 vaccine booster dose // 1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

Main analysis | Restricting to people with ≥1 negative lab test at enrolment | with no tests in the 7  days before enrollment |Censoring matched pairs 7 days after the control receives a booster rather than 0 days | Using date of PCR test result rather than subtracting 2 days | Selecting matched controls without replacement | Exact matching by age (year by year vs 5-year groups) | Restricting events to PCR test.
