---
title: "Análisis de supervivencia"
output: 
  html_document:
    code_folding: show
    highlight: espresso
    css: 
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes  
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3     
editor_options: 
  chunk_output_type: inline
---


```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                       dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center", 
                      fig.width = 12,
                      fig.height = 12)
```

```{r librerias, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
suppressMessages(source_rmd("0_b_funciones.rmd"))
}

```

# Tablas de resultados

***

```{r}
# cargar datos-----------------------------------------------------------------
matching_fcv1 <- readRDS(file.path("Resultados",
        "matching_fcv1.RDS"))

matching_fcv1_domi <- readRDS(file.path("Resultados",
        "matching_fcv1_domi.RDS"))

```

# Programar la replicación completa del articulo

***

## Table 1: Baseline characteristics of the matched study population



<br>

```{r}
hacer_tabla_1 <- function(tt_tibble) {

  
tt_tibble <- matching_fcv1$tt_tibble
    
  tabla_basal_edad <- hacer_basal_discreta(base = tt_tibble,
                                         variable = p_edad_cat_label,
                                         relabel = c(
                                      "0-39",
                                     "40-44", 
                                     "45-49",
                                     "50-54",
                                     "55-59",
                                     "60-64",
                                     "65-69",
                                     "70-74",
                                     "75-79",
                                     "80-84",
                                     "85-89",
                                     "&ge; 90")
                                     ) %>% 
    filter(Variable != "0-39")

  tabla_basal_sexo <- hacer_basal_discreta(base = tt_tibble,
                                         variable = gen,
                                         relabel = c(
                                           "Men",
                                           "Women")
                                         )
                                         
  tabla_basal_n_test <- hacer_basal_discreta(base = tt_tibble,
                                         variable = n_0,
                                         relabel = c(
                                           "0",
                                           "1",
                                           "2",
                                           "&ge; 3")
                                         )

  tabla_basal_vaccine_type <- hacer_basal_discreta(base = tt_tibble,
                                         variable = tvc1_label,
                                         relabel = NULL
                                         )

  
  tabla_basal_booster_type <- hacer_basal_discreta(base = tt_tibble,
                                         variable = tvc3,
                                         relabel = NULL
                                         ) %>% 
    mutate(`0` = NA) %>% 
    filter(Variable != "<NA>")

  tabla_basal_t_pauta_comp <- hacer_basal_discreta(tt_tibble %>% 
    mutate(
      t_desde_pauta_completa = 90 + temp_var,
      t_desde_pauta_completa_cat = case_when(
        between(t_desde_pauta_completa, 91, 150) ~  "91-150 days",
        between(t_desde_pauta_completa, 151, 180) ~ "151-180 days",
        t_desde_pauta_completa > 180 ~  "&ge; 181 days"),
      t_desde_pauta_completa_cat = factor(t_desde_pauta_completa_cat,
        levels = c("91-150 days", "151-180 days", "&ge; 181 days"))),
    variable = t_desde_pauta_completa_cat)

  tabla_basal <- bind_rows(
                           tabla_basal_edad,
                           tabla_basal_sexo,
                           tabla_basal_n_test,
                           tabla_basal_vaccine_type,
                           tabla_basal_booster_type,
                           tabla_basal_t_pauta_comp) %>% 
    select(-Total)
  
  
  n_unexposed <- tt_tibble %>% 
    filter(exposicion == 0) %>%
    nrow()
    
  n_exposed <- tt_tibble %>% 
    filter(exposicion == 1) %>%
    nrow()
  
  id_uniques <- tt_tibble %>% 
    filter(exposicion == 0) %>%
    distinct(id) %>%
    nrow()
  
  
  kable(tabla_basal, align = c("c"), escape = FALSE,
      col.names = c("Variable",
                    glue("No booster group (n = {n_unexposed}*)"),
                    glue("Booster group (n = {n_exposed})")),
      table.attr = "style = \"color: black;\"",
      caption = "Baseline characteristics of the matched study population") %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "condensed"),
                full_width = FALSE, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "white", background = "dodgerblue",
           extra_css = "vertical-align:middle") %>% 
  pack_rows("Age group (years), n (%)", 1, 11) %>%
  pack_rows("Sex, n (%)", 12, 13) %>%
  pack_rows("Number of previous SARS-CoV-2 tests, n (%)", 14, 17) %>%
  pack_rows("Primary vaccine schedule, n (%)", 18, 21) %>%
  pack_rows("Booster dose, n (%)", 22, 23) %>%
  pack_rows("Time since primary vaccine schedule, n (%)", 24, 26) %>%  
  footnote(footnote_as_chunk = TRUE, 
           general = glue("NA = not applicable, *{id_uniques} unique individuals in the no booster group."))

  }

```

<br>

```{r}
# ejecutar la función para hacer la tabla--------------------------------------
tabla_1_matching_fcv1 <- hacer_tabla_1(tt_tibble = matching_fcv1$tt_tibble)

tabla_1_matching_fcv1

```

<br>

## Table 2: Estimated effectiveness of an mRNA COVID-19 vaccine booster in individuals* who had completed primary vaccination schedule against COVID-19

Analyses based on 2 083 857 matched pairs who remained under follow-up by day 7 after the booster dose. Overall, Age group (years): [40–59, 60–79, ≥80], Sex, Type of previous vaccination, Time since vaccination completed, Type of booster [mRNA-1273,BNT162b2]
 # Booster group [Events| Risk per 10 000 individuals] No booster group [Events| Risk per 10 000 individuals]  1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

```{r}

diftime_match <- matching_fcv1$tt_tibble %>% 
  mutate(survtime = date_end - date_start) %>% 
  # filter(survtime >= 7) %>% 
  group_by(target_trial_number, par) %>% 
  summarise(dif = max(survtime)-min(survtime)) %>% 
  ungroup()

diftime_match %>% arrange(desc(dif))

matching_fcv1$tt_tibble %>% filter(!is.na(fdef),
                                   fdef - date_start < 34)

matching_fcv1$tt_tibble %>% filter(target_trial_number == 12,
                                   par == 304)

# 1044184

```


## Table 3: Sensitivity analyses of vaccine effectiveness 7–34 days after an mRNA COVID-19 vaccine booster dose // 1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

Main analysis | Restricting to people with ≥1 negative lab test at enrolment | with no tests in the 7  days before enrollment |Censoring matched pairs 7 days after the control receives a booster rather than 0 days | Using date of PCR test result rather than subtracting 2 days | Selecting matched controls without replacement | Exact matching by age (year by year vs 5-year groups) | Restricting events to PCR test.
