---
title: "Análisis de supervivencia"
output: 
  html_document:
    code_folding: show
    highlight: espresso
    css: 
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes  
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3     
editor_options: 
  chunk_output_type: inline
---


```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                       dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center", 
                      fig.width = 12,
                      fig.height = 12)
```

```{r librerias, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
suppressMessages(source_rmd("0_b_funciones.rmd"))
}

```

```{r}
# cargar datos-----------------------------------------------------------------
matching_fcv1 <- readRDS(file.path("Resultados",
        "matching_fcv1.RDS"))

matching_fcv1_domi <- readRDS(file.path("Resultados",
        "matching_fcv1_domi.RDS"))

```

# Table 2: Estimated effectiveness of an mRNA COVID-19 vaccine booster in individuals* who had completed primary vaccination schedule against COVID-19

***


```{r}
# hacer tabla 2----------------------------------------------------------------
hacer_tabla_2 <- function(tt_tibble, 
                          tiempo_efecto = 7) {

# arreglar tibble
  tt_tibble_after_7_days <- tt_tibble %>% 
  # filtrar parejas con seguimiento después del día 7
      mutate(survtime = date_end - date_start) %>% 
      group_by(target_trial_number, par) %>% 
      filter(min(survtime) >= tiempo_efecto) %>%
      ungroup() %>% 
  # crear tiempo desde pauta completa
      mutate(
        t_desde_pauta_completa = 90 + temp_var,
        t_desde_pauta_completa_cat = case_when(
          between(t_desde_pauta_completa, 91, 195) ~  "91-195 days",
          between(t_desde_pauta_completa, 196, 220) ~ "196-220 days",
        t_desde_pauta_completa > 221 ~  "&ge; 221 days"),
        t_desde_pauta_completa_cat = factor(t_desde_pauta_completa_cat,
          levels = c("91-195 days", "196-220 days", "&ge; 221 days")))

  tt_tibble_after_7_days_pairs <- tt_tibble_after_7_days %>% 
    filter(exposicion == 1) %>% nrow()

# hacer estratos tabla 2
  table2_overall <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days, 
    group_description = "Overall",
    number_of_bootstrap = 500)

  table2_grupo_edad_1 <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(p_edad_cat_label %in% c(
        "[40,45)",	
        "[45,50)",		
        "[50,55)")), 
    group_description = "40-54",
    number_of_bootstrap = 500)

  table2_grupo_edad_2 <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(min(survtime) >= tiempo_efecto) %>%
      ungroup() %>% 
      filter(p_edad_cat_label %nin% c(
        "[40,45)",	
        "[45,50)",		
        "[50,55)")), 
    group_description = "&ge; 55",
    number_of_bootstrap = 500)

  table2_hombre <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(gen == 1), 
    group_description = "Male",
    number_of_bootstrap = 500)

  table2_mujer <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(gen == 2), 
    group_description = "Female",
    number_of_bootstrap = 500)

  table2_vac_pfizer <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(tvc1_label == "BioNTech/Pfizer"), 
    group_description = "BioNTech/Pfizer",
    number_of_bootstrap = 500)

  table2_vac_janssen <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(tvc1_label == "J&J / Janssen"), 
    group_description = "J&J / Janssen",
    number_of_bootstrap = 500)

  table2_vac_moderna <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(tvc1_label == "Moderna/Lonza"), 
    group_description = "Moderna/Lonza",
    number_of_bootstrap = 500)

  table2_vac_az <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(tvc1_label == "Oxford/AstraZeneca"), 
    group_description = "Oxford/AstraZeneca",
    number_of_bootstrap = 500)
  
  table2_tsv1 <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(t_desde_pauta_completa_cat == "91-195 days"), 
    group_description = "91-195 days",
    number_of_bootstrap = 500)

  table2_tsv2 <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(t_desde_pauta_completa_cat == "196-220 days"), 
    group_description = "196-220 days",
    number_of_bootstrap = 500)

  table2_tsv3 <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days %>% 
      filter(t_desde_pauta_completa_cat == "&ge; 221 days"), 
    group_description = "&ge; 221 days",
    number_of_bootstrap = 500)

# para el booster el filtrado es algo más complicado
  ids_pfizer <- tt_tibble_after_7_days %>% 
  # seleccionar booster pfizer
    filter(exposicion == 1,
         tvc3 == "BioNTech/Pfizer") %>% 
    select(target_trial_number, par)
# seleccionar todas las parejas de booster pfizer
  tt_tibble_after_7_days_pfizer <- tt_tibble_after_7_days %>% 
    semi_join(ids_pfizer)

  ids_moderna <- tt_tibble_after_7_days %>% 
  # seleccionar booster pfizer
    filter(exposicion == 1,
         tvc3 == "Moderna/Lonza") %>% 
    select(target_trial_number, par)
# seleccionar todas las parejas de booster pfizer
  tt_tibble_after_7_days_moderna <- tt_tibble_after_7_days %>% 
    semi_join(ids_moderna)

  table2_tvc3_pfizer <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days_pfizer, 
    group_description = "BioNTech/Pfizer",
    number_of_bootstrap = 500)

  table2_tvc3_moderna <- hacer_grupo_tabla_2(
    tt_tibble = tt_tibble_after_7_days_moderna, 
    group_description = "Moderna/Lonza",
    number_of_bootstrap = 500)

  # ensamblar tabla 2
  table2_ensambled <- bind_rows(
    table2_overall,
    table2_grupo_edad_1,
    table2_grupo_edad_2,
    table2_hombre,
    table2_mujer,
    table2_vac_pfizer,
    table2_vac_janssen,
    table2_vac_moderna,
    table2_vac_az,
    table2_tsv1,
    table2_tsv2,
    table2_tsv3,
    table2_tvc3_pfizer,
    table2_tvc3_moderna)
  
 # kable table 2  
 kable(table2_ensambled, align = c("c"), escape = FALSE,
      col.names = c(" ",
                    "Events",
                    "Risk per 10 000 individuals",
                    "Events",
                    "Risk per 10 000 individuals",
                    " ",
                    " "),
      table.attr = "style = \"color: black;\"",
      caption = "Estimated effectiveness of an mRNA COVID-19 vaccine booster in individuals* who had completed primary vaccination schedule against COVID-19") %>%
   add_header_above(c(" ",
                      "No booster group" = 2, 
                      "Booster group" = 2, 
                      "1–risk ratio (95% CI)", 
                      "Risk difference per 10 000 individuals (95% CI)"),
                    bold = T, color = "white", background = "dodgerblue",
           extra_css = "vertical-align:middle") %>% 
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "condensed"),
                full_width = FALSE, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "white", background = "dodgerblue",
           extra_css = "vertical-align:middle") %>% 
  pack_rows("Age group (years)", 2, 3) %>%
  pack_rows("Sex", 4, 5) %>%
  pack_rows("Type of previous vaccination", 6, 9) %>%
  pack_rows("Time since vaccination completed", 10, 12) %>%  
  pack_rows("Type of booster", 13, 14) %>%
  footnote(footnote_as_chunk = TRUE, 
           general = glue("Analyses based on {tt_tibble_after_7_days_pairs} matched pairs who remained under follow-up by day 7 after the booster dose"))
}


```

```{r}
# ejecutar la función para hacer la tabla--------------------------------------
tabla_2_matching_fcv1 <- hacer_tabla_2(tt_tibble = matching_fcv1$tt_tibble)

tabla_2_matching_fcv1

```


## Table 3: Sensitivity analyses of vaccine effectiveness 7–34 days after an mRNA COVID-19 vaccine booster dose // 1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

Main analysis | Restricting to people with ≥1 negative lab test at enrolment | with no tests in the 7  days before enrollment |Censoring matched pairs 7 days after the control receives a booster rather than 0 days | Using date of PCR test result rather than subtracting 2 days | Selecting matched controls without replacement | Exact matching by age (year by year vs 5-year groups) | Restricting events to PCR test.
