---
title: "Análisis de supervivencia"
output: 
  html_document:
    code_folding: show
    highlight: espresso
    css: 
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes  
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3     
editor_options: 
  chunk_output_type: inline
---


```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                       dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center", 
                      fig.width = 12,
                      fig.height = 12)
```

```{r librerias, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
suppressMessages(source_rmd("0_b_funciones.rmd"))
}

```


```{r}
# cargar datos-----------------------------------------------------------------
matching_fcv1 <- readRDS(file.path("Resultados",
        "matching_fcv1.RDS"))

matching_fcv1_domi <- readRDS(file.path("Resultados",
        "matching_fcv1_domi.RDS"))

```


# Table 3: Sensitivity analyses of vaccine effectiveness 7–34 days after an mRNA COVID-19 vaccine booster dose // 1–risk ratio (95% CI) | Risk difference per 10 000 individuals (95% CI)

***

Main analysis | Restricting to people with ≥1 negative lab test at enrolment | with no tests in the 7  days before enrollment |Censoring matched pairs 7 days after the control receives a booster rather than 0 days | Using date of PCR test result rather than subtracting 2 days | Selecting matched controls without replacement | Exact matching by age (year by year vs 5-year groups) | Restricting events to PCR test.

```{r}

```

