---
title: "Supplementary Material. Correspondence: Booster Long-term effectiveness against infection and severe cases on Omicron-dominant period in Navarra"
author: 
 - Francisco Sanchez-Saez, FISABIO, sanchez_frasae@gva.es
 - Ibai Tamayo, NAVARRABIOMED
 - Julian Librero, NAVARRABIOMED
date: "`r format(Sys.Date())`"
bookdown::html_document2:
    keep_md: false 
    theme: cerulean
    highlight: breezedark
    css: style.css
    anchor_sections: false
    toc: no
bibliography: References.bib
csl: tl.csl
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
suppressMessages(source_rmd("0_b_funciones.rmd"))
}

```

```{r}
# cargar datos-----------------------------------------------------------------

# modelo 1. infección por características
matching_fcv1_longer_34 <- readRDS(file.path("Resultados",
        "matching_fcv1_longer_34.RDS"))
matching_fcv1_longer_70 <- readRDS(file.path("Resultados",
        "matching_fcv1_longer_70.RDS"))

# modelo 1. infección por domicilio
matching_fcv1_domi_34 <- readRDS(file.path("Resultados",
        "matching_fcv1_domi_34.RDS"))
matching_fcv1_domi_70 <- readRDS(file.path("Resultados",
        "matching_fcv1_domi_70.RDS"))

# modelo 3. hospitalización por edad y sexo
matching_fih1_longer_34_bis <- readRDS(file.path("Resultados",
        "matching_fih1_longer_34_bis.RDS"))
matching_fih1_longer_70_bis <- readRDS(file.path("Resultados",
        "matching_fih1_longer_70_bis.RDS"))

# cargar resultados------------------------------------------------------------
rr_m1_34 <- readRDS(file.path("Resultados", "rr_m1_34.RDS"))
rr_m1_70 <- readRDS(file.path("Resultados", "rr_m1_70.RDS"))
rr_m2_34 <- readRDS(file.path("Resultados", "rr_m2_34.RDS"))
rr_m2_70 <- readRDS(file.path("Resultados", "rr_m2_70.RDS"))
rr_m4_34 <- readRDS(file.path("Resultados", "rr_m4_34.RDS"))
rr_m4_70 <- readRDS(file.path("Resultados", "rr_m4_70.RDS"))

```

# Results

***

In this population cohort study, we linked data from three population registries in Navarra (Vaccination Registry, Laboratory Results Registry, and BARDENA-Population registry) to select community-dwelling individuals aged 40 years or older Who completed their primary vaccine schedule at least 3 months before the start of follow-up, and had not tested positive for SARS-CoV-2 since the start of the pandemic, excluding  educational workers, health-care workers, and nursing home residents [@Bardena2022]. We conducted three different target trial emulations.

a) Target trial for ascertaining booster effectiveness against infections from 2022-01-04 to 2022-03-31. Matching each boostering day (from 2022-01-03 to 2022-03-30) by age, sex, previous negative test, primary vaccine type and date, health basic zone, migrant status, flu vaccinated in 2020 and in 2021, and household members.

b) Target trial for ascertaining booster effectiveness against infections from 2022-01-04 to 2022-03-31. Matching each boostering day (from 2022-01-03 to 2022-03-30) by home address.

c) Target trial for ascertaining booster effectiveness against hospitalisations due to COVID-19 from 2022-01-04 to 2022-06-13. Matching each boostering day (from 2022-01-03 to 2022-06-12) by age, sex, and comorbidities (diabetes mellitus, coronary artery disease, chronic kidney failure, chronic obstructive pulmonary disease, hyperdyslipidemia, hypertension, stroke, and obesity).

Individuals characteristics in each of the three target trials are presented in Tables \@ref(tab:tabla1a), \@ref(tab:tabla1b), and \@ref(tab:tabla1c).

<br>

```{r tabla1a}
# ejecutar la función para hacer la tabla--------------------------------------
table_1_m1 <- hacer_tabla_1(tt_tibble = matching_fcv1_longer_70$tt_tibble)
table_1_m1 

```

<br>

```{r tabla1b}
table_1_m2 <- hacer_tabla_1(tt_tibble = matching_fcv1_domi_70$tt_tibble,
                            adaptada = "Yes")

table_1_m2
```

< br>

```{r tabla1c}
table_1_m4 <- hacer_tabla_1(tt_tibble = matching_fih1_longer_70_bis$tt_tibble)

table_1_m4

```

<br<

# References

***
