---
title: "Target Trial: Booster Long-term effectivity against infection and severe cases on Omicron-dominant period in Navarra"
author: "Francisco Sánchez Sáez"
date: "`r format(Sys.Date())`"
output: 
  bookdown::html_document2:
    keep_md: true 
    theme: cerulean
    highlight: breezedark
    css: style.css
    anchor_sections: false
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      code_folding: show
    toc_depth: 3
bibliography: References.bib
csl: tl.csl
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


#  Introduction

***

The long-term effectivity against infection and severe cases of the booster vaccination is assessed on Omicron-dominant period in Navarra. This has been done following the **Target trial emulation** methodology [@Danaei2013]. The results of infections from January 3 to February 6 are compared with [@Monge2022] and then the period of the study is enlarged in order to assess the long-term effects.

# Comparison

***

<a href="https://www.sciencedirect.com/science/article/pii/S1473309922002924">   Effectiveness of mRNA vaccine boosters against infection with the SARS-CoV-2 omicron (B.1.1.529) variant in Spain: a nationwide cohort study </a>


## Background

The omicron (B.1.1.529) variant of SARS-CoV-2 has increased capacity to elude immunity and cause breakthrough infections. The aim of this study was to estimate **the effectiveness of mRNA-based vaccine boosters (third dose) against infection with the omicron variant by:




## Methods

In this population cohort study, we linked data from three population registries in Navarra (Vaccination Registry, Laboratory Results Registry, and BARDENA-Population registry) to select

  * community-dwelling individuals aged 40 years or older, 
  * who completed their primary vaccine schedule at least 3 months before the start of follow-up, and
  * had not tested positive for SARS-CoV-2 since the start of the pandemic. 
  
On each day between Jan 3, and Feb 6, 2022, we matched:

  * individuals who received a booster mRNA vaccine and controls of the same 
      - Age (5-years group).

- Sex.

- Number of previous negative test (0,1,2,3+).

- Type of primary vaccine (homologous or Janssen).

- Time since complete vaccination.

- Type of booster.

- Basic zone.

- Migrant.

- Flu vaccine (2020).

- Flu vaccine (2021).

- Number of people at home.
      
We estimated risk of laboratory-confirmed SARS-CoV-2 infection using the Kaplan-Meier method and compared groups using risk ratios (RR) and risk differences. Vaccine effectiveness was calculated as one minus RR.
  
## Results

In [1] Overall, the estimated effectiveness from day 7 to 34 after a booster was 51·3% (95% CI 50·2–52·4).

```{r tabla1}
tabla1 <- readRDS(file.path("Resultados", "tabla_1_matching_fcv1.RDS"))

tabla1

```

```{r tabla2}
tabla2 <- readRDS(file.path("Resultados", "tabla_2_matching_fcv1.RDS"))

tabla2

```

```{r tabla3}
tabla3 <- readRDS(file.path("Resultados", "tabla_3.RDS"))

tabla3
  
```

# References

***
