---
title: "Target Trial: Booster Long-term effectivity against infection and severe cases on Omicron-dominant period in Navarra"
author: "Francisco Sánchez Sáez"
date: "`r format(Sys.Date())`"
output: 
  bookdown::html_document2:
    keep_md: false 
    theme: cerulean
    highlight: breezedark
    css: style.css
    anchor_sections: false
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      code_folding: show
    toc_depth: 3
bibliography: References.bib
csl: tl.csl
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# source("0_a_librerias.R")
# ya se cargan cuando se carguen las funciones

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# función para cargar un .Rmd como si se hiciese source de un .r---------------
source_rmd = function(file, ...) {
  tmp_file = tempfile(fileext = ".R")
  on.exit(unlink(tmp_file), add = TRUE)
  knitr::purl(file, output = tmp_file)
  source(file = tmp_file, ...)
}

```

```{r echo=FALSE, message=FALSE, include=FALSE, warning=FALSE}
# cargar funciones de 0_funciones----------------------------------------------
if (!exists("se_ha_cargado_f")) {
suppressMessages(source_rmd("0_b_funciones.rmd"))
}

```

#  Introduction

***

The omicron (B.1.1.529) variant of SARS-CoV-2 has increased capacity to elude immunity and cause breakthrough infections. The long-term effectivity against infection and severe cases of the booster vaccination is assessed on Omicron-dominant period in Navarra. This has been done following the **Target trial emulation** methodology [@Danaei2013]. The results of infections from January 3 to February 6 are compared with [@Monge2022] and then the period of the study is enlarged in order to assess the long-term effects.

# Methods

***

In this population cohort study, we linked data from three population registries in Navarra (Vaccination Registry, Laboratory Results Registry, and BARDENA-Population registry) to select:

  - Non-residents.
  
  - Non-educational workers.
  
  - Non health-care workers.

  - Community-dwelling individuals aged 40 years or older. 
  
  - Who completed their primary vaccine schedule at least 3 months before the start of follow-up.
  
  - Had not tested positive for SARS-CoV-2 since the start of the pandemic. 
  
On each day between Jan 3, and Feb 6, 2022, we matched individuals who received a booster mRNA vaccine and controls of the same: 

- Age (5-years group).

- Sex.

- Number of previous negative test (0,1,2,3+).

- Type of primary vaccine (homologous or Janssen).

- Time since complete vaccination.

- Type of booster.

- Basic zone.

- Migrant.

- Flu vaccine (2020).

- Flu vaccine (2021).

- Number of people at home.
      
We estimated risk of laboratory-confirmed SARS-CoV-2 infection using the Kaplan-Meier method and compared groups using risk ratios (RR) and risk differences. **Vaccine effectiveness was calculated as one minus RR**.
  
# Results

***

## Comparison

In the study of Omicron in Spain [@Monge2022], the estimated effectiveness from day 7 to 34 after a booster was 51·3% (95% CI 50·2–52·4).

In Navarra, we have the following results shown in Tables \@ref(tab:tabla1), \@ref(tab:tabla2) and \@ref(tab:tabla3). 

<br>

```{r}
# cargar datos-----------------------------------------------------------------
matching_fcv1 <- readRDS(file.path("Resultados",
        "matching_fcv1.RDS"))
matching_fcv1_sens0 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens0.RDS"))
matching_fcv1_sens1 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens1.RDS"))
matching_fcv1_sens2 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens2.RDS"))
matching_fcv1_sens3 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens3.RDS"))
matching_fcv1_sens4 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens4.RDS"))
matching_fcv1_sens5 <- readRDS(file.path("Resultados",
        "matching_fcv1_sens5.RDS"))

```


```{r tabla1, include=FALSE, eval=TRUE}
tabla1 <- hacer_tabla_1(matching_fcv1$tt_tibble)

```

```{r}
tabla1

```

<br>

```{r tabla2, include=FALSE, eval=TRUE}
set.seed(1)
tabla2 <- hacer_tabla_2(matching_fcv1$tt_tibble, 
                        tiempo_efecto = 7)
```


```{r}
tabla2

```

<br>

```{r tabla3, include=FALSE, eval=TRUE}
set.seed(1)
tabla3 <- hacer_tabla_3()

```


```{r}

tabla3
  
```

<br>

## Long-term infection (fcv1)

Now, the period has been extended from January 3 to April 13 and 60 days of follow-up has been selected. The results are shown in Tables \@ref(tab:t1-fcv1-longer) and \@ref(tab:t2-fcv1-longer)

```{r}
# guardar resultados-----------------------------------------------------------
matching_fcv1_longer <- readRDS(file.path("Resultados",
        "matching_fcv1_longer.RDS"))

```

<br>

```{r}
# análisis---------------------------------------------------------------------
f_analisis(lista = matching_fcv1_longer,
           tiempo_efecto = 7,
           lim_1 = 0.80,
           lim_zoom = 0.9)

```

<br>

```{r t1-fcv1-longer}
t1_fcv1_longer <- hacer_tabla_1(matching_fcv1_longer$tt_tibble)

t1_fcv1_longer

```

<br>

```{r t2-fcv1-longer, include=FALSE, eval=TRUE}
set.seed(1)
t2_fcv1_longer <- hacer_tabla_2(matching_fcv1_longer$tt_tibble)

```

```{r}
t2_fcv1_longer

```

<br>

## Long-term infection (fih1)

Now, the period has been extended from January 3 to April 13 and 60 days of follow-up has been selected. The results are shown in Tables \@ref(tab:t1-fih1-longer) and \@ref(tab:t2-fih1-longer)

```{r}
# guardar resultados-----------------------------------------------------------
matching_fih1_longer <- readRDS(file.path("Resultados",
        "matching_fih1_longer.RDS"))

```

<br>

```{r}
# análisis---------------------------------------------------------------------
f_analisis(lista = matching_fih1_longer,
           tiempo_efecto = 7,
           lim_1 = 0.997,
           lim_zoom = 0.998)

```

<br>

```{r t1-fih1-longer}
t1_fih1_longer <- hacer_tabla_1(matching_fih1_longer$tt_tibble)

t1_fih1_longer

```

<br>

```{r t2-fih1-longer, include=FALSE, eval=TRUE}
set.seed(1)
t2_fih1_longer <- hacer_tabla_2(matching_fih1_longer$tt_tibble)

```


```{r }
t2_fih1_longer

```

<br>

# References

***
